\vspace{-2cm}Supplementary material: \\Sky Tomography for 3D Aerosol Distribution Recovery

### 2013-07-11 supplementary.tex
Basically the iccp2013 in the optics express template

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%% preamble %%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[10pt,letterpaper]{article}

\usepackage{opex3}
\usepackage{times}
\usepackage{graphicx}
\graphicspath{{./images/}}
\usepackage{epstopdf}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\usepackage{bm}
\usepackage{enumerate}

%\usepackage{ae} %%for Computer Modern fonts

@@

\newcommand{\yoavcomment}[1]{}
\renewcommand{\yoavcomment}[1]{#1} % Comment to remove images

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%% begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%% title page information %%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Sky Tomography for 3D Aerosol Distribution Recovery}

\author{Amit~Aides and Yoav~Y.~Schechner and Vadim~Holodovsky}

\address{Electrical Engineering Dept., Technion - Israel Inst. Tech., \\ Haifa 32000, Israel}

\email{amitibo@tx.technion.ac.il} %% email address is required

% \homepage{http:...} %% author's URL, if desired

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%% abstract and OCIS codes %%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% [use \begin{abstract*}...\end{abstract*} if exempt from copyright]

\begin{abstract}
  Aerosols effect climate, health and aviation.  Currently, their
  retrieval assumes a plane-parallel atmosphere and solely vertical
  radiative transfer. We propose a principle to recover the atmosphere
  as it really is: a three dimensional (3D), volumetric, transparent
  huge object. Tomography is the key to recovery. The process involves
  acquiring the sky lightfield by multi-view wide-angle photography on
  a very large scale. The tomography model is distinct, as the light
  source is unidirectional and uncontrolled, while off-axis scattering
  dominates the images.  We formulate an image formation model based
  on 3D radiative transfer. Model inversion is done using optimization
  methods, exploiting a closed-form gradient which we derive for the
  model-fit cost function. The problem is complex but tractable and
  parallelizable, eventually estimating the 3D aerosol distribution.
\end{abstract}

\ocis{(000.0000) General.} % REPLACE WITH CORRECT OCIS CODES FOR YOUR ARTICLE

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%% References %%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliography{article}{}
\bibliographystyle{osajnl}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%  body  %%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
\label{sec:intro}

Lightfield and integral imaging~\cite{bishop,horstmeyer,kim,Ng1948}
samples the optical radiance distribution in location and
direction. It is mainly used in small-scale setups. This paper deals
with a huge scale, up to Earth's size.  The atmosphere allows light to
pass through in multiple locations and directions. Light is affected
by this medium. Therefore, in this paper we lay out a principle to
recover this 3D medium using measured and modeled lightfields
(Fig.~\ref{fig:front}).
\begin{figure}[t!]
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/front_img.pdf}}
  \caption{\small The sky is photographed from multiple viewpoints
    using wide angle (hemispherical) cameras, in a very wide area. The
    three dimensional distribution of aerosols in the atmosphere
    affects the images. This distribution is then recovered by a
    dedicated tomography formulation.}
  \label{fig:front}
\end{figure}

Projecting this large object to various directions is similar to
tomography in other scientific domains. However, the formulation here
is distinct. Most tomography setups have a controlled and/or
multidirectional radiation source~\cite{gorbunov,messer}. In contrast,
our source is the uncontrolled, unidirectional Sun. Moreover, typical
tomography relies on a linear model~\cite{gregson}: the pixel value is
a linear combination of components along a line of sight (LOS), or a
multiplicative combination (linearized by a logarithm). Linear
tomography can detect volcanic gas~\cite{wright}, which absorbs
UV. Other gases in the atmosphere absorb IR. However, in visible
light, atmospheric attenuation is typically dominated by {\em
  scattering} by particles (aerosols), rather than absorption by
gasses. Thus, in our problem, we cannot rely on direct illumination,
but on sunlight scattered into the LOS.  The model turns out to be
{\em nonlinear, yet tractable}.

We do not deal with clouds here. Clouds scatter sunlight very strongly
and are easily observed. Hence they are directly recovered using
common stereoscopic tools, similarly to opaque surfaces~\cite{seiz}.
On the other hand, aerosols have much more subtle visual effects and
are thus more difficult to recover. We focus on them.  In remote
sensing~\cite{diner}, imaging through air is associated with {\em
  atmospheric correction}, based on {\em aerosol retrieval}. In this
discipline, the atmosphere is often assumed to be plane-parallel, for
simplicity, using only 1D vertical radiative transfer. Consequently
state-of-the-art aerosol retrieval is done in distinct large lateral
blocks~\cite{Martonchikc} with limited height
resolution~\cite{kalashnikova}. We, however, seek high resolution 3D
recovery. Computational photography offers new ways to peer into
media. In addition to active descattering~\cite{fuchs,kim,Ng1948} and
recovery of refractive transparent objects~\cite{ihrke}, overcoming
the atmosphere~\cite{Joshi2010,Zhu2013} to view ground objects
was studied in horizontal, fixed
views~\cite{fattal,he,Chen,kratz,narasimhan2,oakley,Hschechner2,tan}. In
this paper, however, the medium itself, at all relevant altitudes is
the object of interest.

3D recovery of this medium has direct implications to various
scientific communities that either rely on remotely-sensed imagery,
study the atmosphere, or overcome the medium to see beyond. These
include meteorology, atmospheric sciences, volcanology, and
climatology.  Aerosol retrieval is important for understanding climate
evolution~\cite{Dayan2008,kalashnikova} and monitoring air
quality. Mapping aerosol density is significant to aviation safety,
which needs real time assessment of conditions and visibility around
flight paths. To keep safe, today's coarse sensing limits flight
capacity. A prominent example is the 2010 eruption of Iceland's
Eyjafjallaj$\ddot {\rm o}$kull volcano, whose ash (aerosols) covered
much of Europe's airspace, grounding $\approx 100,000$
flights. Knowing the 3D distribution of aerosol density may indicate
safe 3D corridors to safely pass through, enhancing airspace
use. Viewing beyond the medium, atmospheric correction is needed, for
example, in satellite tracking of chlorophyll
distributions~\cite{johnsen}. Additional bodies in the solar system
have atmospheres. These objects can be viewed from multiple directions
by probes.  The approach described here may be helpful there.

We model passive optical tomographic imaging of 3D atmospheric
scatterer distributions in cloudless conditions. Then, we solve this
tomography problem, to recover the distribution. Recovery is
formulated as an optimization that minimizes a cost function. We
derive the gradient of this cost function, to enable efficient
optimization.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \vspace{-0.25cm}
\section{Theoretical Background}
\label{sec:back}
\vspace{-0.2cm}

\noindent {\bf Extinction}: Sun rays (SR) irradiate a small volume
that includes particles of a certain type.  Each particle has an {\em
  extinction cross section} $\sigma$ (units ${\rm m}^2$) for
interacting with the irradiance. The volume includes many particles of
this type. The denser the volume, the stronger is the extinction.  The
density of the particles is $n$ (units $1/{\rm m}^3$). Per unit
volume, the {\em extinction coefficient} $\beta$ (units $1/{\rm m}$)
is
\begin{align}
  \beta= \sigma n \;.
  \label{eq:extinctc}
\end{align}
The volume has infinitesimal length $dl$. Then, the relative portion
of extinct SR irradiance is the unitless differential {\em optical
  depth}
\begin{align}
  d\tau= \beta dl=\sigma n dl \;.
  \label{eq:extinct}
\end{align}
The optical depth aggregates in extended propagation:
\begin{align}
  \tau= \int d\tau=\int \beta dl=\int \sigma n dl \;.
  \label{eq:tau}
\end{align}
Through an attenuating volume, the {\em transmittance} exponentially
decays with the optical depth:
\begin{align}
  t=\exp^{-\tau}
  \label{eq:beer-lambert}
\end{align}

\noindent {\bf Scattering}: Interaction of a single particle with the
irradiance is by absorption and scattering. The weight of scattering
(to all directions), relative to the total extinction is given by the
unitless {\em single scattering albedo} $\varpi$ of the particle. The
{\em scattering coefficient} $\alpha$ (units $1/{\rm m}$) is
\begin{align}
  \alpha= \varpi\beta=\varpi \sigma n \;.
  \label{eq:alph}
\end{align}
Scattering is generally anisotropic. Its angular distribution is
determined by a {\em phase function} $P$. Part of the light scatters
towards a camera's line of sight (LOS), as illustrated in
Fig.~\ref{fig:groundgrid}. The angle between the SR and LOS is the
scattering angle $\Phi^{\rm scatter}$. The phase function $P(\Phi^{\rm
  scatter})$ is normalized: its integral over all solid angles is
unit. The {\em angular scattering coefficient} $\tilde\alpha$ (units
$1/({\rm m}\cdot{{\rm strad}})$) is
\begin{align}
  \tilde\alpha(\Phi^{\rm scatter}) = \varpi\beta P(\Phi^{\rm scatter})
  = \varpi \sigma n P(\Phi^{\rm scatter}).
  \label{eq:alphabasic}
\end{align}

The phase function is often approximated by a parametric expression,
as the Henyey-Greenstein function,
\begin{align}
  P_g(\Phi^{\rm scatter})\approx \frac{3} {8\pi} \frac{(1 -
    g^2)(1+\mu^2)} {(2+g^2)(1 + g^2 - 2g\mu)^\frac{3}{2}}
  \label{eq:aerosol_scatter}
\end{align}
where $g$ is an {\em anisotropy parameter} and
\begin{align}
  \mu\equiv \cos \Phi^{\rm scatter}.
  \label{eq:mu}
\end{align}

\noindent {\bf Air molecules}: Scattering by air molecules follows the
{\em Rayleigh} model: for wavelength $\lambda$ the phase function is
\begin{align}
  P^{\rm air}\left[\mu(k)\right] &= \frac{3}{16\pi}(1+\mu^2)
  \label{eq:rayleighP}
\end{align}
and $\varpi^{\rm air}$=1. Air molecular density $n^{\rm air}$ falls
off approximately exponentially with altitude, with a
characteristic~\cite{Levi1980} falloff height $H^\mathrm{air}=8\
km$. Consequently~\cite{Levi1980}, the coefficients for extinction and
scattering by air molecules are modeled by
\begin{align}
  \alpha^{\rm air}(h, \lambda)=\beta^{\rm air}(h, \lambda) \approxeq
  \frac{1.09 \times 10^{-3}}{\lambda^4}
  \exp(-h/H^\mathrm{air}) %\left[-\frac{h}{H^\mathrm{air}}\right].
  \label{eq:rayleighbeta}
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \vspace{-0.25cm}
\section{Image Acquisition Principle}
\label{sec:setup} \vspace{-0.2cm}

The atmosphere has a non-uniform distribution of scattering
aerosols. We seek to recover this 3D volumetric distribution. To solve
this problem, we formulate a process analogous to tomographic
reconstruction. The scene is projected to multiple directions. Thus, a
system captures integrated radiance as a function of direction and 2D
projected location. Any voxel in the atmosphere contributes to the
integrated radiance in multiple directional measurements
(Fig.~\ref{fig:groundgrid}). The measurements then provide a large
number of constraints, to recover the distribution: the density and
type of aerosols, per voxel.
\begin{figure*}[t!]
  \begin{center}
    \vspace{-0.4cm}
    \includegraphics[width=0.99\linewidth]{images/groundtomog24.eps}
  \end{center}\vspace{-1.5cm}
  \caption{\small Lightfield imaging through a volumetric distribution
    in the atmosphere, using ground-based cameras. Our tomographic
    reconstruction follows the acquisition. The atmosphere is analyzed
    in a voxel grid.}
  \label{fig:groundgrid}
\end{figure*}

Earth's radiation is sampled both spatially and angularly from
space~\cite{breon,diner,Martonchikc,vanMol}. However, current
multiview spaceborne systems are very coarse. For example, aerosol
retrieval in the most complex instrument, MISR, requires spatial
blocks that are about $17\times 17$km wide, each observed from just 9
views along-track. This practically leads to vertical radiative
transfer analysis, degenerating atmospheric analysis to
1D. Experimental airborne instruments under
development~\cite{baxter,dinerDavis10} may provide better, if still
coarse resolution once they are operational.

We believe that high resolution atmospheric recovery can be achieved
by a large set of ground-based wide-angle~\cite{Cossairt2011,
  Peleg01omnistereo:panoramic, Koppal:2011:WMS:2191740.2192152}
sky-cameras, looking upwards and capturing the sky lightfield.
Moreover, satellites image close to the orbit track (a 1D array of
viewpoints). In contrast, land-based cameras can form a 2D set of
viewpoints~\cite{DBLP:journals/pieee/SnavelySGSS10} as easy or hard as
a 1D grid~\cite{Joshi06naturalvideo}. However, before designing and
setting up such a very large scale system requires assessment of many
details that had not been explored. These include camera
specifications needed to recover typical distributions. Hence, a major
theoretic and numerical research phase is ahead.

This paper takes the first step, of formulating this principle and
demonstrating feasibility using realistic simulations. The formulation
of this paper can also apply to multiview images that are captured
from satellites, for future spaceborne instruments of this capacity.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \vspace{-0.25cm}
\section{Forward Model}
\label{sec:skymodel} \vspace{-0.2cm}

This section describes models for image formation. In the consecutive
section, we describe how the image formation is inverted to recover
the 3D sky structure.  Consider Fig.~\ref{fig:groundgrid}.
Ground-based wide-angle sky-cameras capture the sky lightfield from
below. Per viewpoint, the view azimuth and elevation angles (relative
to the zenith and north) are encapsulated in the vector
${\bf{\Theta}}$.  A raw image is $i_{\bf x}({\bf{\Theta}})$: a
camera's location ${\bf x}$ is fixed, while any pixel in a frame
represents an angle ${\bf{\Theta}}$.  The measured radiance in all
locations ${\bf x}$ and angles ${\bf{\Theta}}$ is the {\em lightfield}
$I({\bf x},{\bf{\Theta}})$. Individual images are slices of the
lightfield.
% Alternatively, several ground-based cameras can be mounted on moving
% vehicles, assuming that the aerosol distribution does not change
% much during the time-lapse of the camera trajectory.

Sunlight is scattered in the medium, creating {\em
  airlight}~\cite{fattal,narasimhan2,Hschechner2,tan}. For each view
${\bf{\Theta}}$ and ground location ${\bf x}$, the airlight is
generally different, depending on the distribution of aerosols both
along a LOS, and along the SRs that hit the LOS.  As
Fig.~\ref{fig:groundgrid} shows, different LOSs (distinct ${\bf
  x},{\bf{\Theta}}$) cut through different sets atmospheric
voxels. Thus, for each view, the radiance scattered from a voxel is
attenuated differently, depending on the distribution of aerosols
along the LOS~\cite{hansen}.

A forward model takes as input the aerosol distribution, and outputs images as if captured at various viewpoints. The model calculates radiative transfer, based on fixed parameters as the Sun's characteristics. We use a single scattering model, in which any SR changes direction (scatters) only once on the way to the camera. This model is valid in atmospheres that are not very dense: inside fog and clouds this model does not apply. Under single-scattering approximation, radiative transfer has three steps (Fig.~\ref{fig:groundgrid}):\\

\vspace{-0.35cm}
\noindent
1. Attenuation of a SR propagating from the top of the atmosphere
(TOA) to voxel $k$. \\

\vspace{-0.35cm}
\noindent
2. Light scattering at voxel $k$, towards a camera.\\

\vspace{-0.35cm}
\noindent
3. Light attenuation on the LOS from voxel $k$ to the camera.

\noindent
Steps 1 and 3 involve the optical depth along the light path to and
from voxel $k$, analyzed in Sec.~\ref{sec:optical-depth}.  Step 2
involves the scattering coefficient at voxel $k$, described in
Sec.~\ref{sec:scattering}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Optical Depth}
\label{sec:optical-depth}

An infinitesimal volume contains aerosols. The extinction and
scattering coefficients due to aerosols in this volume are,
respectively
\begin{equation}
  \beta^{\rm aerosol}=\sigma^{\rm aerosol} n^{\rm aerosol}
  \;\;,\;\;
  \alpha^{\rm aerosol}=\varpi^{\rm aerosol} \beta^{\rm aerosol}
  \;.
  \label{eq:betaer}
\end{equation}
In addition, the infinitesimal volume contain also air
molecules. Hence, the overall extinction and scattering coefficients
in this small volume are, respectively
\begin{equation}
  \beta=\beta^{\rm air}+\beta^{\rm aerosol}
  \;\;,\;\;
  \alpha=\alpha^{\rm air}+\alpha^{\rm aerosol}
  \;.
  \label{eq:betair}
\end{equation}

Any voxel generally contains both air molecules and aerosols. Voxels
are indexed by $k$ or $q$. As approximation, assume that within any
voxel, the molecular parameters $\{ \beta^{\rm air}(k),\alpha^{\rm
  air}(k)\}$ and the aerosol parameters $\{ \sigma^{\rm
  aerosol}(k),\varpi^{\rm aerosol}(k), n^{\rm aerosol}(k),g(k)\}$ are
constants, e.g., corresponding to the value at each voxel
center. These parameters may change between voxels.

A voxel's vertical geometric thickness is $\Delta z$.  The Sun zenith
angle is $\Phi^{\rm SR}$. Denote a SR line segment between the TOA and
the center of voxel $k$ by $[{\rm SR},k]$. This SR intersects voxel
$q$. The geometric length of this intersection line segment is $\Delta
z f_{\rm SR}(q)/\cos\Phi^{\rm SR}$: the factor \mbox{$f_{\rm SR}(q)\in
  [0,1]$} expresses how much of the vertical thickness of $q$ is
crossed by the SR. Following Eqs.~(\ref{eq:tau},\ref{eq:betair}), the
optical depth between the TOA and voxel $k$ is
\begin{equation}
  \tau_{\rm SR}(k)=\frac{1}{\cos\Phi^{\rm SR}}
  \sum_{q \in[{\rm SR},k]}
  \beta(q)\Delta z  f_{\rm SR}(q)
  \;\;.
  \label{eq:lSRn}
\end{equation}
Based on Eqs.~(\ref{eq:betaer},\ref{eq:betair},\ref{eq:lSRn}),
\begin{equation}
  \tau_{\rm SR}(k)=
  \tau_{\rm SR}^{\rm air}(k) +  \tau_{\rm SR}^{\rm aerosol}(k)
  \;\;,
  \label{eq:lSRaa}
\end{equation}
where
\begin{equation}
  \tau_{\rm SR}^{\rm air}(k)=\frac{\Delta z}{\cos\Phi^{\rm SR}}
  \sum_{q \in[{\rm SR},k]}
  \beta^{\rm air}(q)  f_{\rm SR}(q)
  \label{eq:lSRair}
\end{equation}
and
\begin{equation}
  \tau_{\rm SR}^{\rm aerosol}(k)=\frac{\Delta z}{\cos\Phi^{\rm SR}}
  \sum_{q \in[{\rm SR},k]}
  \sigma^{\rm aerosol}(q) n^{\rm aerosol}(q) f_{\rm SR}(q)
  \label{eq:lSRaeros}
\end{equation}

The number of voxels is $N_{\rm voxels}$. All their associated
variables are concatenated into columns stack vectors, each $N_{\rm
  voxels}$ long. Aerosol densities and cross sections in all voxels
are stored in the respective vectors ${\bf n}$ and
$\vect{\sigma}$. Define a $N_{\rm voxels}\times N_{\rm voxels}$ sparse
matrix ${\bf D}^{\mathrm{Sun \rightarrow voxel}}$, whose element
$(k,q)$ is
\begin{equation}
  D^{\mathrm{Sun \rightarrow voxel}}(k,q) =
  \left\{
    \begin{array}{ll}
      \frac{\Delta zf_{\rm SR}(q)}{\cos\Phi^{\rm SR}}
      & \mbox{ if $q \in[{\rm SR},k]$} \\
      0  & \mbox{ otherwise}
      \label{eq:Dsv}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
Eqs.~(\ref{eq:lSRaeros},\ref{eq:Dsv}) lead to a vector of SR optical
depths due to aerosols (See Fig.~\ref{fig:optidepth}):
\begin{equation}
  \vect{\tau}_{\rm SR}^{\rm aerosol}=
  {\bf D}^{\mathrm{Sun \rightarrow voxel}}
  (\vect{\sigma} \odot {\bf n})
  \label{eq:tauSRvec1}
\end{equation}
where the operator $\odot$ denotes the Hadamard (element-wise)
product.
\begin{figure}
  \centering
  \yoavcomment{\def\svgwidth{\columnwidth}\input{images/optical_distance.pdf_tex}}
  \caption{\small Irradiance of voxel $k$ is attenuated by voxels
    above it on a SR. The scattered radiance from voxel $k$ is then
    attenuated by voxels below it on a LOS to camera $c$. The overall
    attenuation of any voxel $k$ by all voxels $q$ is equivalent to an
    optical depth affecting $k$. It is formalized in matrix-vector
    operations. }
  \label{fig:optidepth}
\end{figure}
Similarly, Eq.~(\ref{eq:lSRair}) leads to a vector of SR optical
depths due to air, $\vect{\tau}_{\rm SR}^{\rm air}$.

Analogously, for camera $c$, denote by $[{\rm LOS}_c,k]$ a LOS bounded
between the camera and the center of voxel $k$. The LOS zenith angle
is $\Phi^{\rm LOS}_c$.  This LOS intersects voxel $q$. The geometric
length of this intersection line segment is $\Delta z f_{\rm
  LOS_c}(q)/\cos\Phi^{\rm LOS}_c$: the factor $f_{\rm LOS_c}(q)\in
[0,1]$ expresses how much of the vertical thickness of $q$ is crossed
by the LOS.  Analogously to
Eqs.~(\ref{eq:lSRaa},\ref{eq:lSRair},\ref{eq:lSRaeros}), The optical
depth %path length
along a LOS to $k$ is
\begin{equation}
  \tau_{{\rm LOS}_c}(k)=
  \tau_{{\rm LOS}_c}^{\rm air}(k) +  \tau_{{\rm LOS}_c}^{\rm aerosol}(k)
  \;\;,
  \label{eq:lLOSaerot}
\end{equation}
where
\begin{equation}
  \tau_{{\rm LOS}_c}^{\rm air}(k)=\frac{\Delta z}{\cos\Phi^{\rm LOS}_c}
  \sum_{q \in[{\rm LOS}_c,k]}
  \beta^{\rm air}(q)  f_{\rm LOS_c}(q)
  \label{eq:lLOSair}
\end{equation}
and
\begin{align}
  \label{eq:lLOSaeros}
  \tau_{{\rm LOS}_c}^{\rm aerosol}(k)=
  ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ ~~~~~~~~~~~~~~~~~~%\nonumber
  ~~~~~
  \\
  % ~~~~
  \frac{\Delta z}{\cos\Phi^{\rm LOS}_c} \sum_{q \in[{\rm LOS}_c,k]}
  \sigma^{\rm aerosol}(q) n^{\rm aerosol}(q) f_{\rm LOS_c}(q).
  \nonumber
\end{align}
Eq.~(\ref{eq:lLOSaeros}) leads to a vector of LOS optical depths due
to aerosols:
\begin{equation}
  \vect{\tau}_{{\rm LOS}_c}^{\rm aerosol}=
  {\bf D}^{\mathrm{voxel \rightarrow cam}}_c
  (\vect{\sigma} \odot {\bf n})
  \label{eq:tauLOSvec1}
\end{equation}
Here ${\bf D}^{\mathrm{voxel \rightarrow cam}}_c$ is a $N_{\rm
  voxels}\times N_{\rm voxels}$ sparse matrix whose element $(k,q)$ is
\begin{equation}
  D^{\mathrm{voxel \rightarrow cam}}_c(k,q) =
  \left\{
    \begin{array}{ll}
      \frac{\Delta z f_{\rm LOS_c}(q)}{\cos\Phi^{\rm LOS}_c}
      & \mbox{ if $q \in[{\rm LOS}_c,k]$} \\
      0  & \mbox{ otherwise}
      \label{eq:Dvc}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
Similarly, Eq.~(\ref{eq:lSRair}) leads to a vector of LOS optical
depths due to air, $\vect{\tau}_{{\rm LOS}_c}^{\rm air}$.

The fixed sparse matrices ${\bf D}^{\mathrm{Sun \rightarrow voxel}}$
and ${\bf D}^{\mathrm{voxel \rightarrow cam}}_c$ are compounded to a
single matrix
\begin{equation}
  {\bf D}_c=
  {\bf D}^{\mathrm{Sun \rightarrow voxel}}+
  {\bf D}^{\mathrm{voxel \rightarrow cam}}_c
  \;\;.
  \label{eq:Dtotal}
\end{equation}
Similarly, the molecular optical depths along all trajectories between
the sun, each voxel and camera $c$ are compounded to a vector
\begin{equation}
  \vect{\tau}_c^{\rm air}=
  \vect{\tau}_{\rm SR}^{\rm air}+
  \vect{\tau}_{{\rm LOS}_c}^{\rm air}
  \;\;.
  \label{eq:tauairtotal}
\end{equation}
Using Eq.~(\ref{eq:rayleighbeta}) for $\beta^{\rm air}$ in all voxels,
the vector $\vect{\tau}_c^{\rm air}$ is fixed. Thus
$\vect{\tau}_c^{\rm air}$ can be calculated once, per sun zenith
angle.

Using
Eqs.~(\ref{eq:lSRaa},\ref{eq:tauSRvec1},\ref{eq:lLOSair},\ref{eq:tauLOSvec1},\ref{eq:Dtotal},\ref{eq:tauairtotal}),
the total optical depths corresponding to LOSs (of camera $c$) and SRs
that cross all voxels comprise the vector
\begin{equation}
  \vect{\tau}_c= \vect{\tau}_c^{\rm air}
  + {\bf D}_c (\vect{\sigma} \odot {\bf n})
  \;\;.
  \label{eq:tautotal}
\end{equation}
This vector depends on the variables $\vect{\sigma}$ and ${\bf n}$
(See Fig.~\ref{fig:optidepth}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scattering}
\label{sec:scattering}

>>>>

\documentclass[a4paper]{article}

\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}

@@

@@

\title{\vspace{-2cm}Supplementary material: \\Sky Tomography for 3D Aerosol Distribution Recovery}
\author{Paper ID: 19}
\date{}

\maketitle

\section{Gradient Derivation}
\label{sec:gradient-derivation}

Here we detail the derivation of the gradient of the objective
function:
\begin{equation}
  \label{eq:objectiveA}
  F({\bf n})
  = \sum_{c=1}^{N_{\rm views}}
  \| {\bf i}^{\rm measured}_c - {\bf i}_c({\bf n})\|^2_2
\end{equation}
Here ${\bf i}^{\rm measured}_c$ is the image captured by camera $c$
and ${\bf i}_c({\bf n})$ is an image modeled from the viewpoint of
camera $c$ according to the density distribution ${\bf n}$. In the
article we show that ${\bf i}_c({\bf n})$ can be expressed by
\begin{align}
  {\bf i}_c= L^{\rm TOA} {\vect{\Pi}}_c \Big\{ e^{-(\vect{\tau}_c^{\rm
      air} + {\sigma}^{\rm aerosol} {\bf D}_c {\bf n}) }\odot
  \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;
  \nonumber \\
  [\tilde{\vect{\alpha}}^{\rm air}_c + %\right.
  \varpi^{\rm aerosol}\sigma^{\rm aerosol} P^{\rm
    aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bf n} ] \Big\} .
  \label{eq:bigIA}
\end{align}

The gradient of $F$ with respect to ${\bf n}$ is
\begin{align}
  \Grad{{\bf n}} F = -2\sum_{c=1}^{N_{\rm views}}
  \transpose{\left[{\bf J}_{{\bf i}_c}({\bf n})\right]} [{\bf i}^{\rm
    measured}_c - {\bf i}_c({\bf n})] \;.
  \label{eq:gradient1}
\end{align}
Here the matrix ${\bf J}_{{\bf i}_c}({\bf n})$ is the Jacobian of the
vector ${\bf i}_c$ with respect to ${\bf n}$. Element $(\Theta,k)$ of
this matrix differentiates the intensity in pixel ${\bf \Theta}$ (in
viewpoint $c$) with variation of the density at voxel $k$, i.e.,
$\partial i_c({\bf \Theta})/\partial{n^{\rm aerosol}(k)}$.

In order to describe the derivation of the Jacobian ${\bf J}_{{\bf i}_c}({\bf n})$, we first show some results relating to differentiation. Let $\vect{n}$
be a vector of length $q$. Let $\vect{g}(\vect{n})$ be a vector
function: it outputs a vector of length $r$. Let $\mat{B}$ be a $q
\times r$ matrix and
\begin{align}
  \vect{g}(\vect{n}) = \exp^{-\transpose{\mat{B}}\vect{n}}.
  \label{eq:example1}
\end{align}
In Eq.~(\ref{eq:example1}), the exponential is element-wise (not
raising an operator to some power). Then
\begin{align}
  \label{eq:partial2}
  \PartDeriv{\vect{g}}{\vect{n}} &= - \mat{B} \,
  \OpDiag{\exp^{-\transpose{\mat{B}}\vect{n}}}
\end{align}
Here we denote by $\OpDiag{\vect{v}}$ conversion of vector $\vect{v}$
into a diagonal matrix, whose main diagonal elements correspond to the
elements of $\vect{v}$. Using~(\ref{eq:partial2}) we can calculate
\begin{align}
  \label{eq:partial4}
  \PartDeriv{\exp^{-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}
      {\bf D}_c {\bf n})}}
  {\vect{n}} &= - {\sigma}^{\rm aerosol}\transpose{\OpDistance_c} \,
  \OpDiag{\exp^{-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}
      {\bf D}_c {\bf n})}}
\end{align}
In~(\ref{eq:partial4}) we assume that $\vect{\tau}_c^{\rm air}$ is
known and constant.

To calculate the derivative of the Hadamard product
in~(\ref{eq:bigIA}) we first note the following: Let
$\vect{u}(\vect{n})$ be a vector function that outputs a vector of
length $r$. Let $\mat{B}$ be a $r \times q$ matrix. Then,
\begin{align}
  \label{eq:partial1}
  \PartDeriv{\transpose{\mat{B}} (\vect{g} \odot \vect{u})}{\vect{n}}
  = \left[ \PartDeriv{\vect{g}}{\vect{n}} \OpDiag{\vect{u}} +
    \PartDeriv{\vect{u}}{\vect{n}} \OpDiag{\vect{g}} \right] \mat{B}.
\end{align}
Then,
\begin{align}
  \label{eq:partial3}
  \PartDeriv{\, \varpi^{\rm aerosol}\sigma^{\rm aerosol} P^{\rm
      aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bf n}}{\vect{n}}
  =
  \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;
  \nonumber \\
  \varpi^{\rm aerosol}\sigma^{\rm aerosol}\OpDiag{P^{\rm
      aerosol}_g(\vect{\Phi}^{\rm scatter}_c)}
  \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;
\end{align}

Based on~(\ref{eq:partial4},~\ref{eq:partial1})
and~(\ref{eq:partial3}) we can derive a close-form expression for the
Jacobian of~(\ref{eq:bigIA}):
\begin{align}
  {\bf J}_{{\bf i}_c}({\bf n}) &= L^{\rm TOA}({\bf A}-{\bf B}){\bf C}
  ,
  \label{eq:gradient2}
\end{align}
where
\begin{align}
  \label{eq:gradient3}
  {\bf A} &= \varpi^{\rm aerosol}\sigma^{\rm aerosol}
  \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)} \nonumber\\
  {\bf B} &= {\sigma}^{\rm aerosol}\transpose{{\bf D}_c} \nonumber\\
  & \;\;\; \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
      aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
      scatter}_c) \odot{\bf n}
    ]} \nonumber \\
  {\bf C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
      aerosol} {\bf D}_c {\bf n})]} \transpose{{\vect{\Pi}}_c}
\end{align}
